Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-06-28 paper/Analisis.tex
update to the escape fraction section

\begin{figure}
  \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
   \caption{Escape fraction as a function of rotational velcity. The
     continous (dashed) lines correspond to homogeneous (central)
     models.
     \label{fig:efvsv}}
\end{figure}

@@

In Figure \ref{fig:efvsNeufeld} we put these results in the context of
the analytical solution for the infinite slab \citep{Neufeld90} shown
by the continous line. In this setup the analytic solution depends
solely on the product $(a\tau_{\rm   H})^{1/3}\tau_{a}$. This valid
only in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
\ref{fig:efvsNeufeld} corespond to the cases of different
velocities. We observe that in all cases the escape fraction is higher
than in the slab configuration. We also note that for $\tau_{\rm H}=10^{5}$
the escape fraction does not increase as expected, This is
due to the fact that the condition $a\tau_{h}\gg 1$ does not hold.

>>>>

\begin{figure}
  \includegraphics[width=0.45\textwidth]{escapefraction.png}
   \caption{Escape fraction as a function of rotational velcity. The
     continous (dashed) lines correspond to homogeneous (central)
     models.
     \label{fig:efvsv}}
\end{figure}

@@

In Figure \ref{fig:efvsNeufeld} we put these results in the context of
the analytical solution for the infinite slab \citep{Neufeld90}. In
Neufeld's setup the analytic solution depends solely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
\ref{fig:efvsNeufeld} corespond to the cases of different
velocities. We observe that the escape fraction is higher
by factors of $2-10$  than the expected values for the slab
configuration. We also see that for the lower value $\tau_{\rm
  H}=10^{5}$ the escape fraction does not increase with respect to the
solution for $\tau_{\rm H}=10^{6}$ as expected, however we not that we
are in a regime where the condition for the analytic expectations 
($a\tau_{h}\gg 1$) does not hold.
